Regular singular Volterra equations on complex domains

### 2024-04-30 sima/reg-sing-volterra_sima.tex
Revise inclusions between sing-exp spaces

% TikZ libraries
\usetikzlibrary{bbox}
\usetikzlibrary{fadings}

@@

The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}. \textcolor{blue}{We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.}
%%Within $\holo(\domain)$, we define a normed subspace consisting of functions which are uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}
\color{red}
Fixing a real constant $\Lambda$, we restrict our attention to holomorphic functions on $\domain$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$. One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} They form a space $\singexp{0}{\Lambda}(\domain)$, which we equip with the norm $\|f\|_{0,\Lambda} = \sup_\domain e^{-\Lambda|\zeta|}\,|f|$. With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
\par\color{blue}
\begin{definition}\label{def:exp}
For any $\Lambda \in \R$, let
\[ \singexp{0}{\Lambda}(\domain) \subset \holo(\domain) \]
be the subspace consisting of functions $f$ with $f \lesssim e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
\[ \|f\|_{0, \Lambda} := \sup_\Omega e^{-\Lambda|\zeta|}\,|f|. \]
With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
%%\textcolor{orange}{$\{f \in \holo(\domain) : f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}\}$}
The subspace of functions of exponential type $\Lambda$ strictly contains $\singexp{0}{\Lambda}(\domain)$. A function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. Definition~\ref{def:exp} instead requires a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.\end{rmk}
We now relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
For any $\sigma, \Lambda \in \R$, let
\[ \singexp{\sigma}{\Lambda}(\domain) \subset \holo(\domain) \]
be the subspace consisting of functions $f$ with $f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]
The inclusion $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is again continuous.
For $\Lambda\in\R$, let 
\[\|f\|_{0,\Lambda} := \sup_\domain e^{-\Lambda|\zeta|}\,|f|\,,\qquad f\in\holo(\domain)\,.\]
    We define the normed space
    \[\singexp{0}{\Lambda}(\domain):=\{ f\in\holo(\domain) : \|f\|_{0,\Lambda}<+\infty\}\,.\]
    The space $\singexp{0}{\Lambda}(\domain)$ can be seen as the space of functions uniformly bounded by constant multiples of $e^{\Lambda |\zeta|}$.
With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
\begin{proposition}\label{exp-complete}
The space $\singexp{\sigma}{\Lambda}(\domain)$ is complete.
Take a Cauchy sequence $(f_j)_{j \in \N}$ in $\singexp{\sigma}{\Lambda}(\domain)$. This sequence is Cauchy in $\holo(\domain)$ as well, because the inclusion map $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is bounded with respect to each of the seminorms on $\holo(\domain)$ given by $f \mapsto \sup_K |f|$ for compact subsets $K \subset \domain$. Since $\holo(\domain)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\domain)$ will always converge in the topology of $\holo(\domain)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

The Cauchy property in $\singexp{\sigma}{\Lambda}(\domain)$ says that for any $r > 0$, there is some $n$ for which $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$. Since convergence in $\holo(\domain)$ implies pointwise convergence, it follows that $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f - f_n| \le r$. This reasoning shows that $(f_j)_{j \in \N}$ converges to $f$ in the norm $\|\cdot\|_{\sigma, \Lambda}$. It also shows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we have
\begin{align*}
|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_n| \\
& \le r + \|f_n\|_{\sigma,\Lambda}
\end{align*}
for the corresponding $n$, so $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f|$ is bounded.
\end{proof}
\color{red}
\begin{proposition}%%\label{exp-complete}
The space $\singexp{0}{\Lambda}(\domain)$ is complete.
\end{proposition}
\begin{proof}
Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$. The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $|f| \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$, so our sequence is Cauchy in $\holo(\Omega)$ too. Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ implies that for any $r > 0$, \textcolor{red}{we can find some} there exists $n$ for which $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$. Since convergence in $\holo(\Omega)$ implies pointwise convergence, \textcolor{red}{we can see as $k$ grows that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$} we get that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$, as $k$ grows. This shows that \textcolor{red}{our} the sequence $f_k$ converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$. \textcolor{red}{We can also see} In addition, from this argument it follows that $f$ is in $\singexp{0}{\Lambda}(\domain)$: picking some $r > 0$, we observe that
\begin{align*}
e^{-\Lambda |\zeta|}\,|f| & \le e^{-\Lambda |\zeta|}\,|f - f_n| + e^{-\Lambda |\zeta|}\,|f_n| \\
& \le r + \|f_n\|_{0,\Lambda}
\end{align*}
for the corresponding $n$, showing that $e^{-\Lambda |\zeta|}\,|f|$ is bounded.
\end{proof}\color{black}

\textcolor{pink}{Now, let us relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.} \color{red} For any $\sigma \in \R$, let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$. Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$. Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we \textcolor{red}{can} generalize Proposition~\ref{exp-complete}:
\color{brown}
For $\sigma\in\R$, let 
\[\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|\,,\qquad f\in\holo(\domain)\,.\]
\begin{definition}
    We define the normed space
    \[\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega):=\{f\in\holo(\domain)\,\vert \, \|f\|_{\sigma,\Lambda}<+\infty\}\,.\]
\end{definition}
\begin{rmk}
    The above is a space of functions uniformly bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda |\zeta|}$.
\end{rmk}
\color{black}
\color{pink}\begin{proposition}
The space $\singexp{\sigma}{\Lambda}(\Omega)$ is complete.
\end{proposition}
\color{brown}
\begin{proof}
Let $\{f_n\}_{n=1}^\infty\subset\singexp{\sigma}{\Lambda}(\domain)$ be a Cauchy sequence. The inclusion map $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each norm on $\sup_K |f|$ on $\holo(\domain)$, where $K \subset \Omega$ is compact. Hence, $\{f_n\}_{n=1}^\infty$ is a Cauchy sequence also in $\holo(\domain)$. The latter being complete~\cite[Proposition~3.5]{fnl-cpx-anal}, the sequence converges to a function $f\in\holo(\domain)$.

By the Cauchy property on $\singexp{\sigma}{\Lambda}(\Omega)$, for any $r > 0$ there exists $n$ such that $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ for every $k \ge n$. Since convergence in $\holo(\Omega)$ implies pointwise convergence, we get that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$, as $k$ grows. This implies that the sequence $\{f_n\}_{n=1}^\infty$ converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$. In addition, from this argument it follows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we observe that
\begin{align*}
|\zeta|^{-\sigma}e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_n| \\
& \le r + \|f_n\|_{\sigma,\Lambda}
\end{align*}
for the corresponding $n$, showing that $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f|$ is bounded.
\end{proof}
\color{black}
\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
\begin{proposition}\label{prop:inclus-ge-exp}
If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{proposition}
\begin{proof}
By definition,
\[ \|f\|_{\sigma,\Lambda}=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|. \]
The norm $\|\cdot\|_{\sigma, \Lambda'}$ is designed to give $|f| \le |\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}$, implying that
\begin{align*}
\|f\|_{\sigma,\Lambda} & \leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&\leq \|f\|_{\sigma,\Lambda'}.
\end{align*}
In the last step, we use the assumption that $\Lambda' \le \Lambda$.
\end{proof}
\textcolor{blue}{One might describe the functions in $\singexp{\sigma}{\Lambda}(\domain)$ as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} Taking the union of these spaces over all $\Lambda \in \R$, we get the subspace that contains all exponential-type functions which are bounded by constant multiples of $|\zeta|^\sigma$ near zero.}

\textcolor{violet}{As we mentioned in Section~\ref{sec:fn-space-defs} [now removed]}\textcolor{pink}{, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.}\footnote{\textcolor{orange}{[footnote moved because of rephrasing above]} \textcolor{pink}{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}}
For any $\sigma \in \R$, we define $\singexpalg{\sigma}(\domain)$ as the union
\[ \bigcup_{\Lambda\in\R}\singexp{\sigma}{\Lambda}(\domain) \]

@@

\color{red}

@@

\color{brown}
For every $\Lambda'$, there is a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ obtained by choosing $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$.

>>>>

% TikZ libraries
\usetikzlibrary{bbox}
\usetikzlibrary{fadings}
\usetikzlibrary{cd}

@@

The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}. \color{blue}We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.
\begin{definition}\label{def:unif-exp}
For any $\Lambda \in \R$, let
\[ \singexp{0}{\Lambda}(\domain) \subset \holo(\domain) \]
be the subspace consisting of functions $f$ with $f \lesssim e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
\[ \|f\|_{0, \Lambda} := \sup_\Omega e^{-\Lambda|\zeta|}\,|f|. \]
\end{definition}
With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
%%\textcolor{orange}{$\{f \in \holo(\domain) : f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}\}$}
\begin{rmk}
The subspace of functions of exponential type $\Lambda$ strictly contains $\singexp{0}{\Lambda}(\domain)$. A function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. Definition~\ref{def:unif-exp} instead requires a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.\end{rmk}
We now relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
\begin{definition}
For any $\sigma, \Lambda \in \R$, let
\[ \singexp{\sigma}{\Lambda}(\domain) \subset \holo(\domain) \]
be the subspace consisting of functions $f$ with $f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]
\end{definition}
The inclusion $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is again continuous.
\begin{proposition}\label{exp-complete}
The space $\singexp{\sigma}{\Lambda}(\domain)$ is complete.
\end{proposition}
\begin{proof}
Take a Cauchy sequence $(f_j)_{j \in \N}$ in $\singexp{\sigma}{\Lambda}(\domain)$. This sequence is Cauchy in $\holo(\domain)$ as well, because the inclusion map $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is bounded with respect to each of the seminorms on $\holo(\domain)$ given by $f \mapsto \sup_K |f|$ for compact subsets $K \subset \domain$. Since $\holo(\domain)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\domain)$ will always converge in the topology of $\holo(\domain)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

The Cauchy property in $\singexp{\sigma}{\Lambda}(\domain)$ says that for any $r > 0$, there is some $n$ for which $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$. Since convergence in $\holo(\domain)$ implies pointwise convergence, it follows that $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f - f_n| \le r$. This reasoning shows that $(f_j)_{j \in \N}$ converges to $f$ in the norm $\|\cdot\|_{\sigma, \Lambda}$. It also shows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we have
\begin{align*}
|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_n| \\
& \le r + \|f_n\|_{\sigma,\Lambda}
\end{align*}
for the corresponding $n$, so $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f|$ is bounded.
\end{proof}
\color{black}
\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
\begin{proposition}\label{prop:inclus-ge-exp}
If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{proposition}
\begin{proof}
By definition,
\[ \|f\|_{\sigma,\Lambda}=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|. \]
The norm $\|\cdot\|_{\sigma, \Lambda'}$ is designed to give $|f| \le |\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}$, implying that
\begin{align*}
\|f\|_{\sigma,\Lambda} & \leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&\leq \|f\|_{\sigma,\Lambda'}.
\end{align*}
In the last step, we use the assumption that $\Lambda' \le \Lambda$.
\end{proof}
%\textcolor{blue}{One might describe the functions in $\singexp{\sigma}{\Lambda}(\domain)$ as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}
\color{blue}

The union $\bigcup_{\Lambda \in \R} \singexp{0}{\Lambda}(\domain)$ is the subspace comprising all functions of exponential type. The continuous inclusions between the $\singexp{0}{\Lambda}(\domain)$ define a limit topology on this subspace. The spaces $\singexp{\sigma}{\Lambda}(\domain)$ fit together analogously for other $\sigma \in \R$.
\begin{definition}\label{def:exp-top}
For any $\sigma \in \R$, let $\singexpalg{\sigma}(\domain)$ be the union
\[ \bigcup_{\Lambda \in \R} \singexp{\sigma}{\Lambda}(\domain) \]

@@

For each $\Lambda'$, we define a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ by choosing some $\Lambda > \Lambda'$ and composing the continuous inclusions
\begin{center}
\begin{tikzcd}[column sep=25mm, labels={inner sep=0.75ex}]
\singexp{\sigma'}{\Lambda'}(\domain) \arrow[r, hook, "\text{\footnotesize Proposition~\ref{prop:inclus-lt-pow-gt-exp}}"'] & \singexp{\sigma}{\Lambda}(\domain) \arrow[r, hook, "\text{\footnotesize Definition~\ref{def:exp-top}}"'] & \singexpalg{\sigma}(\domain).
\end{tikzcd}
\end{center}
For any $\Lambda'' < \Lambda'$, the inclusions
\begin{center}
\begin{tikzcd}[row sep=6mm, column sep=8mm, labels={inner sep=0.75ex}]
\singexp{\sigma'}{\Lambda''}(\domain) \arrow[rr, hook, "\text{\footnotesize Proposition~\ref{prop:inclus-ge-exp}}"] \arrow[rd, hook] & & \singexp{\sigma'}{\Lambda'}(\domain) \arrow[ld, hook] \\
& \singexpalg{\sigma}(\domain)
\end{tikzcd}
\end{center}
%%\begin{center}
%%\begin{tikzcd}[row sep=2mm, column sep=15mm, labels={inner sep=1ex,}]
%%\singexp{\sigma'}{\Lambda'}(\Omega) \arrow[rd, hook] \\
%%& \singexpalg{\sigma}(\Omega) \\
%%\singexp{\sigma'}{\Lambda''}(\Omega) \arrow[ru, hook] \arrow[uu, hook, "\text{\footnotesize Proposition~\ref{prop:inclus-ge-exp}}"]
%%\end{tikzcd}
%%\end{center}
automatically commute, because as non-topological linear maps they are all inclusions between subspaces of $\holo(\domain)$. The existence of the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$ then follows from the universal property of the limit topology.
\par\color{red}

@@

For every $\Lambda'$, there is a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ obtained by choosing $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$.
